Tweets

### 2020-04-11 Rmd/tweets.Rmd
added code to parse tweet texts

>>>>

## Parse json file

```{r}
library(magrittr)
```

```{r}
tweets <- rtweet::parse_stream("../data/2020-04-09 16:31:44-tweets.json") %>%
  dplyr::filter(lang == "en") %>%
  tidytext::unnest_tokens(output = word, input = text)
```

## Prepare document-term matrix from tweet words

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
```

```{r}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
library(tidytext)
word_counts <- tweets %>% 
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```
